### 2023-10-02 doc/_fitness_model.qmd
implement Madhav's suggestions

Empirically, the barcode relative frequency trajectories follow an exponential
function of the form [@levy2015; @kinsler2020; @ascensao2023]
$$
f_{t+1}^{(b)} = f_{t}^{(b)} \mathrm{e}^{(s^{(b)} - \bar{s}_t)\tau},
$${#eq-fitness}
where $f_{t}^{(b)}$ is the frequency of barcode $b$ at the end of cycle number
$t$, $s^{(b)}$ is the relative fitness with respect to the reference
strain---the quantity we want to infer from the data---$\bar{s}_t$ is the mean
fitness of the culture at the end of cycle number $t$, and $\tau$ is the time
pass between cycle $t$ and $t+1$. We can rewrite @eq-fitness as
$$
\frac{1}{\tau}\ln \frac{f_{t+1}^{(b)}}{f_{t}^{(b)}} = (s^{(b)} - \bar{s}_t).
$${#eq-logfreq}
@eq-logfreq separates the measurements---the barcode frequencies---from the
unobserved (sometimes referred to as latent) parameters we want to infer from
the data---the population mean fitness and the barcode relative fitness. This is
ultimately the functional form used in our inference pipeline. Therefore, the
relative fitness is computed by knowing the log frequency ratio of each barcode
throughout the growth-dilution cycles.

@@

Our ultimate objective is to infer the relative fitness $s^{(m)}$ for each of
the $M$ relevant barcodes in the experiment. To do so, we account for the three
primary sources of uncertainty in our model:

>>>>

Empirically, each barcode frequency trajectory follows an exponential function
of the form [@levy2015; @kinsler2020; @ascensao2023]
$$
f_{t+1}^{(b)} = f_{t}^{(b)} \mathrm{e}^{(s^{(b)} - \bar{s}_t)\tau},
$${#eq-fitness}
where $f_{t}^{(b)}$ is the frequency of barcode $b$ at the end of cycle number
$t$, $s^{(b)}$ is the relative fitness with respect to the reference
strain---the quantity we want to infer from the data---$\bar{s}_t$ is the mean
fitness of the culture at the end of cycle number $t$, and $\tau$ is the time
pass between cycle $t$ and $t+1$. We can rewrite @eq-fitness as
$$
\frac{1}{\tau}\ln \frac{f_{t+1}^{(b)}}{f_{t}^{(b)}} = (s^{(b)} - \bar{s}_t).
$${#eq-logfreq}
@eq-logfreq separates the measurements---the barcode frequencies---from the
unobserved (sometimes referred to as latent) parameters we want to infer from
the data---the population mean fitness and the barcode relative fitness. This is
ultimately the functional form used in our inference pipeline. Therefore, the
relative fitness is computed by knowing the log frequency ratio of each barcode
throughout the growth-dilution cycles.

@@

Our ultimate objective is to infer the relative fitness $s^{(b)}$ for each of
the $M$ relevant barcodes in the experiment---hereafter referred to as $s^{(m)}$
to distinguish from the general $s^{(b)}$ and the neutral lineages $s^{(n)}$
relative fitness. To do so, we account for the three primary sources of
uncertainty in our model:
